Methodology for Assessing the State of the Practice for Domain X

### 2020-10-11 StateOfPractice/Methodology/Methodology.tex
updated Section 3 of Methodology

\begin{enumerate}
\item Start with state of practice research questions. (Section~\ref{ResearchQuestions}) \pmi{To be completed}
\item Identify the domain. (Section~\ref{SecIdentifyDomain}) \pmi{To be completed based on suggestions}
\item \emph{Domain Experts}: Create a top ten list of software packages in the domain. (\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Meeting Agenda withmDomainmExperts.pdf}{Meeting Agenda with Domain Experts})
\item Brief the Domain Experts on the overall objective, research proposal, research questions, measurement template, survey for short list projects, usability tests, performance benchmarks, maintainability experiments. (\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Meeting Agenda withmDomainmExperts.pdf}{Meeting Agenda with Domain Experts})
\item Identify broad list of candidate software packages in the domain. (Section~\ref{SecIdentifyCandSoft}) \pmi{To be reviewed}
\item Preliminary filter of software packages list. (Section~\ref{SecInitialFilter}) \pmi{To be reviewed}
\item \emph{Domain Experts}: Review domain software list. (\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Meeting Agenda withmDomainmExperts.pdf}{Meeting Agenda with Domain Experts})
\item Domain Analysis. (Section~\ref{SecDomainAnalysis})\pmi{To be reviewed}
\item \emph{Domain Experts}: Vet domain analysis. (\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Meeting Agenda withmDomainmExperts.pdf}{Meeting Agenda with Domain Experts}) \pmi{This was part of the original Steps in Assessing Quality list. We need to add it to the Meeting Agenda}
\item Gather source code and documentation for each prospective software package.
\item Collect empirical measures. (Section~\ref{SecEmpiricalMeasures}) \pmi{To be completed - go over how to clean this up in meeting, or through an issue}
\item Measure using measurement template. (Section~\ref{SecShallowMeasure}) \pmi{To be reviewed}
\item Use AHP process to rank the software packages. (Section~\ref{SecAHP}) \pmi{To be reviewed}
\item Identify a short list of top software packages, typically four to six, for deeper exploration according to the AHP rankings of the measurements.
\item \emph{Domain Experts}: Vet AHP ranking and short list. (\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Meeting Agenda withmDomainmExperts.pdf}{Meeting Agenda with Domain Experts})
\item With short list:
\begin{enumerate}
\item Survey developers (\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Questions to Developers.pdf}{Questions to Developers})
\item Usability experiments (\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/User Experiments.pdf}{User Experiments})
\item Performance benchmarks\pmi{note: this is still in consideration}
\item Maintainability experiments\pmi{note: these experiments need to be completed - to be discussed at next meeting}
\end{enumerate}
\item Rank short list. (Section~\ref{SecRankShortList}) \pmi{To be completed}
\item Document answers for research questions.
\end{enumerate}

>>>>

\begin{enumerate}
\item Start with state of practice research questions. (Section~\ref{ResearchQuestions}) \pmi{To be updated based on feedback}
\item Identify the domain. (Section~\ref{SecIdentifyDomain}) \pmi{In second review}
\item \emph{Domain Experts}: Create a top ten list of software packages in the domain. (\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Meeting Agenda withmDomainmExperts.pdf}{Meeting Agenda with Domain Experts})
\item Brief the Domain Experts on the overall objective, research proposal, research questions, measurement template, survey for short list projects, usability tests, performance benchmarks, maintainability experiments. (\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Meeting Agenda withmDomainmExperts.pdf}{Meeting Agenda with Domain Experts})
\item Identify broad list of candidate software packages in the domain. (Section~\ref{SecIdentifyCandSoft})
\item Preliminary filter of software packages list. (Section~\ref{SecInitialFilter}) \pmi{To be edited based on feedback}
\item \emph{Domain Experts}: Review domain software list. (\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Meeting Agenda withmDomainmExperts.pdf}{Meeting Agenda with Domain Experts})
\item Domain Analysis. (Section~\ref{SecDomainAnalysis})\pmi{To be edited - add intro}
\item \emph{Domain Experts}: Vet domain analysis. (\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Meeting Agenda withmDomainmExperts.pdf}{Meeting Agenda with Domain Experts}) 
\item Gather source code and documentation for each prospective software package.
\item Collect empirical measures. (Section~\ref{SecEmpiricalMeasures})
\item Measure using measurement template. (Section~\ref{SecShallowMeasure}) \pmi{To be edited based on feedback}
\item Use AHP process to rank the software packages. (Section~\ref{SecAHP})
\item Identify a short list of top software packages, typically four to six, for deeper exploration according to the AHP rankings of the measurements.
\item \emph{Domain Experts}: Vet AHP ranking and short list. (\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Meeting Agenda withmDomainmExperts.pdf}{Meeting Agenda with Domain Experts})
\item With short list:
\begin{enumerate}
\item Survey developers (\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Questions to Developers.pdf}{Questions to Developers})
\item Usability experiments (\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/User Experiments.pdf}{User Experiments})
\item Performance benchmarks\pmi{note: this is still in consideration}
\item Maintainability experiments\pmi{note: these experiments need to be completed - to be discussed at next meeting}
\end{enumerate}
\item Rank short list. (Section~\ref{SecRankShortList}) \pmi{To be completed}
\item Document answers for research questions.
\end{enumerate}
